Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Changed section on our proposal

\subsection{Resource offers and bidding}
Periodically, when there are resources currently available, the master will
send a \emph{resource offer} message to all registered frameworks to invite them
to participate in an upcoming auction. Each framework then submits a package of
bids, which we can consider a function of the form
\[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
where there are $n$ slaves, $\mathbf{T}$ is a task (containing an amount of desired
resources on a single slave) and $\mathbf{R}$ is the willingness to pay for the
list of tasks $\mathbf{T}^n$.

A naive representation of this function would use an exponential amount of
space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
independently. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\begin{itemize}
  \item A list of \emph{task packages}, with the assumption that the willingness
    to pay for any subset of the list is simply the sum of the willingness to
    pay for each element in the subset
  \item A list of tasks in each task package, with a specific slave and a
    willingness to pay for each task. The auction assumes that the framework
    desires only one of the tasks and values all of them equally.
\end{itemize}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to, e.g., pay more to have a task run on a faster
machine than a slower one.

@@

\paragraph{Paying more or less} To modify the 
default policy to accomodate inhomogeneous resources,
times, or tasks, we can simply modify framework's
bids to adjust for the desirability of the resource being
purchased or the importance of the purpose they are being used for.

>>>>

\subsection{Resource offers and bidding}
Periodically, when there are resources currently available, the master will
send a \emph{resource offer} message to all registered frameworks to invite them
to participate in an upcoming auction. Each framework then submits a package of
bids, which we can consider a function of the form
\[ \mathcal{B}: \Pi_{i=1}^n R_i \rightarrow \mathbf{R}. \]
where $n$ is the number of slaves, 
$R_i$ is the space of possible resource assignments on slave $i$,
and the value $\mathcal{B}\left(R_1, R_2, \ldots, R_n\right)$ is the framework's
willingness to pay in order to receive resources $R_i$ on slave $i$ for each $i$.

A naive representation of this function would use an exponential amount of
space. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\begin{itemize}
  \item A list of \emph{tasks}, with the assumption that a framework's
    willingness to pay for any set of tasks is simply the total
    willingness to pay for tasks in that set.
  \item For each task a list of possible resources which can be used to perform
    that task, together with a willingness to pay for that set of resources.
\end{itemize}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to cover all of the applications we allude to
in the paper---to handle dealdines, inhomogeneous resources, fragmentation,
tasks of differing priorities, and so on.

@@

\paragraph{Adjusting bids} To modify the 
default policy to accomodate inhomogeneous resources,
times, or tasks, we can simply modify framework's
bids to adjust for the desirability of the resource being
purchased or the importance of the purpose they are being used for.
